### 2015-02-05 cav-2015-tex/rw.tex
Updated the related work to talk about CLP based heap reasoning schemes.

>>>>

A number of constraint-based programming techniques are capable of reasoning about heaps~\cite{Degrave:2010,Charreteur:2009,Albert:2013}. Most notably, the technique in~\cite{Albert:2013} is capable of reasoning about dereferencing operations in a per-path set of unknown input heaps. However, none of these methods provide guarantees about the precision of the analysis performed, nor is it obvious that such guarantees are possible.
